Viz Creation

### 2021-04-21 code/Viz Creation.Rmd
fixed issue
Update Viz Creation.Rmd

```{r}
pew <- pew %>% mutate(sumKnowFactor = dum, .after = sumKnow134789)

@@

>>>>

```{r}
dum <- as_factor(pew$sumKnow134789)
pew <- pew %>% mutate(sumKnowFactor = dum, .after = sumKnow134789)

@@

```{r, echo = echoVal, warning= F, message = F}

pew <- pew %>% mutate(HOMEASSIST1_num = ifelse(HOMEASSIST1_W49 == "Yes", yes = 1, 
                                         ifelse(HOMEASSIST1_W49 == "No", yes = 0, no  = NA)))
pew %>% drop_na(DATAUSEd_num) %>%  
  ggplot(aes(x= propKnow134789, y=DATAUSEd_num)) +
  geom_jitter(aes(color = DATAUSEd_num), alpha=.3, size =1, height = .1, width = .005)+
  geom_smooth(method = "glm",
    method.args = list(family = "binomial"), se = T, color ='black') +
  # scale_color_manual(values = c('blue','red'))+
  theme_bw()
```

```{r}

pew <- pew %>% mutate(DATAUSEd_num = ifelse(DATAUSEd_W49 == "Acceptable", yes = 1, 
                                         ifelse(DATAUSEd_W49 == "Unacceptable", yes = 0, 
                                                ifelse(DATAUSEd_W49 == "Not sure", yes = -1, no  = NA))),
                      DATAUSEd_fct = as_factor(DATAUSEd_W49))
pew %>% drop_na(DATAUSEd_num) %>% filter(DATAUSEd_num != -1) %>%  
  ggplot(aes(x= propKnow134789, y=DATAUSEd_num)) +
  geom_jitter(aes(color = DATAUSEd_fct), alpha=.3, size =1, height = .1, width = .005)+
  geom_smooth(method = "glm",
    method.args = list(family = "binomial"), se = T, color ='black') +
  # scale_color_manual(values = c('blue','red'))+
  theme_bw()

```
